A publishing infrastructure for AI-assisted academic authoring

### 2023-07-17 latex/manuscript.tex
remove automatic generation message from latex
improve table 1

This manuscript
was automatically generated
on July 11, 2023.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1905}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5476}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2619}}@{}}
\caption{\textbf{Manuscripts used to evaluate the AI-based revision workflow.} The title and keywords of a manuscript are used in prompts for revising paragraphs. IDs are used in the text to refer to them, and they link to their GitHub repositories. \label{tbl:manuscripts}}\label{tbl:manuscripts}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Manuscript ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Title
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Keywords
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Manuscript ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Title
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Keywords
\end{minipage} \\
\midrule()
\endhead
\href{https://github.com/greenelab/ccc-manuscript}{CCC} & An efficient not-only-linear correlation coefficient based on machine learning & correlation coefficient, nonlinear relationships, gene expression \\
\href{https://github.com/greenelab/phenoplier_manuscript}{PhenoPLIER} & Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms & genetic studies, functional genomics, gene co-expression, therapeutic targets, drug repurposing, clustering of complex traits \\
\href{https://github.com/greenelab/manubot-gpt-manuscript}{Manubot-AI} & A publishing infrastructure for AI-assisted academic authoring & manubot, artificial intelligence, scholarly publishing, software \\
\bottomrule()
\end{longtable}

@@

We enabled the Manubot AI revision workflow in the GitHub repositories of the three manuscripts (CCC:\linebreak \texttt{https://github.com/greenelab/ccc-manuscript}, PhenoPLIER: \texttt{https://github.com/greenelab/phenoplier\_manuscript}, Manubot-AI: \texttt{https://github.com/greenelab/manubot-gpt-manuscript}).
This added the ``ai-revision'' workflow to the ``Actions'' tab of each repository.
We triggered the workflow manually and used the three language models described above to produce one pull request (PR) per manuscript and model.
These PRs can be accessed from the ``Pull requests'' tab of each repository.
They are titled \emph{``GPT (MODEL) used to revise manuscript''} with \emph{MODEL} being the identifier of the model used.
The PRs show the differences between the original text and the AI-based revision suggestions.
We discuss below our findings based on these PRs across different sections of the manuscripts.

>>>>

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1467}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2822}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3767}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1944}}@{}}
\caption{\textbf{Manuscripts used to evaluate the AI-based revision workflow.} The title and keywords of a manuscript are used in prompts for revising paragraphs. IDs are used in the text to refer to them, and they link to their GitHub repositories. \label{tbl:manuscripts}}\label{tbl:manuscripts}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Manuscript ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub URL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Title
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Keywords
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Manuscript ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub URL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Title
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Keywords
\end{minipage} \\
\midrule()
\endhead
CCC & \href{https://github.com/greenelab/ccc-manuscript}{greenelab/ccc-manuscript} & An efficient not-only-linear correlation coefficient based on machine learning & correlation coefficient, nonlinear relationships, gene expression \\
PhenoPLIER & \href{https://github.com/greenelab/phenoplier_manuscript}{greenelab/phenoplier\_manuscript} & Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms & genetic studies, functional genomics, gene co-expression, therapeutic targets, drug repurposing, clustering of complex traits \\
Manubot-AI & \href{https://github.com/greenelab/manubot-gpt-manuscript}{greenelab/manubot-gpt-manuscript} & A publishing infrastructure for AI-assisted academic authoring & manubot, artificial intelligence, scholarly publishing, software \\
\bottomrule()
\end{longtable}

@@

We enabled the Manubot AI revision workflow in the GitHub repositories of the three manuscripts (CCC, PhenoPLIER, and Manubot-AI).
This added the ``ai-revision'' workflow to the ``Actions'' tab of each repository.
We triggered the workflow manually and used the three language models described above to produce one pull request (PR) per manuscript and model.
These PRs can be accessed from the ``Pull requests'' tab of each repository.
They are titled \emph{``GPT (MODEL) used to revise manuscript''} with \emph{MODEL} being the identifier of the model used.
The PRs show the differences between the original text and the AI-based revision suggestions.
We discuss below our findings based on these PRs across different sections of the manuscripts.
